---
title: "Exercise 14"
author: "Cameron Bale"
format: docx
---

We'll be using the roomba survey data for this exercise. Roomba has asked us to train a model to classify customers into two segments, one that combines `own` and `shopping`, and one for `considering`. Your task is to compare the performance of logistic regression and a decision tree to find the best model for the client.

1. Use `case_when()` to combine the `own` and `shopping` segments into a single category.
2. Use workflows to combine the cleaning attitudes and demographics we've used in class and fit both a logistic regression and a decision tree. Which one has better predictive fit?
3. Try and tune the decision tree hyperparameters to improve its predictive fit.
4. Render the Quarto document into Word and upload to Canvas.

**Five points total, one point each for:**

- **Using `case_when()` to create a binary outcome.**
- **Build a recipe using cleaning attitudes and demographics.**
- **Use a workflow to run a logistic regression and a decision tree and compare accuracy.**
- **Try and improve predictive fit by tuning the hyperparameters on the decision tree.**
- **Submitting a rendered Word document.**

## Data Prep and Feature Engineering

We are encoding `segment` as two categories so that logistic regression becomes an option again.

```{r}
# Load packages.
library(tidyverse)
library(tidymodels)

# Set a seed.
set.seed(42)

# Import data.
roomba_survey <- read_csv("roomba_survey.csv")

# Wrangle S1 into segment.
roomba_survey <- roomba_survey |> 
  rename(segment = S1) |> 
  mutate(
    segment = case_when(
      segment == 1 ~ "own or shopping",
      segment == 3 ~ "own or shopping",
      segment == 4 ~ "considering"
    ),
    segment = factor(segment)
  )

# Split data based on segment.
roomba_split <- initial_split(roomba_survey, prop = 0.75, strata = segment)

# Feature engineering.
roomba_recipe <- training(roomba_split) |>
  recipe(
    segment ~ CleaningAttitudes_1 + CleaningAttitudes_2 + CleaningAttitudes_3 + 
      CleaningAttitudes_4 + CleaningAttitudes_5 + CleaningAttitudes_6 + 
      CleaningAttitudes_7 + CleaningAttitudes_8 + CleaningAttitudes_9 + 
      CleaningAttitudes_10 + CleaningAttitudes_11 +
      D1Gender + D2HomeType + D3Neighborhood + D4MaritalStatus
  ) |>
  step_dummy(all_nominal(), -segment)
```

## Logistic Regression and Decision Trees

We'll create a single workflow and then update it for subsequent models.

```{r}
# Logistic regression.
roomba_lr <- logistic_reg() |> 
  set_engine(engine = "glm")

# Decision tree.
roomba_dt <- decision_tree() |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

# Create a workflow for lr.
roomba_wf_lr <- workflow() |> 
  add_recipe(roomba_recipe) |> 
  add_model(roomba_lr)

# Create a workflow for dt.
roomba_wf_dt <- roomba_wf_lr |> 
  update_model(roomba_dt)

# Fit models.
fit_wf_lr <- fit(roomba_wf_lr, data = training(roomba_split))
fit_wf_dt <- fit(roomba_wf_dt, data = training(roomba_split))

# Compare model accuracy.
model_fit <- bind_cols(
  tibble(model = c("lr", "dt")),
  bind_rows(
    fit_wf_lr |> 
      predict(new_data = testing(roomba_split)) |>
      bind_cols(testing(roomba_split)) |>
      accuracy(truth = segment, estimate = .pred_class),
    fit_wf_dt |> 
      predict(new_data = testing(roomba_split)) |>
      bind_cols(testing(roomba_split)) |>
      accuracy(truth = segment, estimate = .pred_class),
  )
)

model_fit
```

With my initial split, logistic regression performs better! Let's look at the confusion matrices.

```{r}
# Compute a confusion matrix.
fit_wf_lr |>
  predict(new_data = testing(roomba_split)) |>
  bind_cols(testing(roomba_split)) |>
  conf_mat(truth = segment, estimate = .pred_class)

# Compute a confusion matrix.
fit_wf_dt |>
  predict(new_data = testing(roomba_split)) |>
  bind_cols(testing(roomba_split)) |>
  conf_mat(truth = segment, estimate = .pred_class)
```

Each model is providing similar predictions, but the decision tree is mis-predicting some observations as own or shopping that are actually just considering.

## Hyperparameter Tuning

Let's see if we can improve the model fit by tuning the decision tree hyperparameters.

```{r}
# Decision tree hyperparameter tuning.
roomba_dt_02 <- decision_tree(tree_depth = 5) |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

roomba_dt_03 <- decision_tree(tree_depth = 15) |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

roomba_dt_04 <- decision_tree(tree_depth = 25) |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

roomba_dt_05 <- decision_tree(min_n = 5) |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

roomba_dt_06 <- decision_tree(min_n = 15) |> 
  set_engine(engine = "rpart") |> 
  set_mode("classification")

# Pipe a modified workflow right into fit.
fit_wf_dt_02 <- roomba_wf_dt |> 
  update_model(roomba_dt_02) |> 
  fit(data = training(roomba_split))

fit_wf_dt_03 <- roomba_wf_dt |> 
  update_model(roomba_dt_03) |> 
  fit(data = training(roomba_split))

fit_wf_dt_04 <- roomba_wf_dt |> 
  update_model(roomba_dt_04) |> 
  fit(data = training(roomba_split))

fit_wf_dt_05 <- roomba_wf_dt |> 
  update_model(roomba_dt_05) |> 
  fit(data = training(roomba_split))

fit_wf_dt_06 <- roomba_wf_dt |> 
  update_model(roomba_dt_06) |> 
  fit(data = training(roomba_split))

# Compare model accuracy.
bind_rows(
  model_fit,
  bind_cols(
    tibble(model = c(
      "tree_depth = 5", "tree_depth = 10", "tree_depth = 15",
      "min_n = 5", "min_n = 15"
    )),
    bind_rows(
      fit_wf_dt_02 |> 
        predict(new_data = testing(roomba_split)) |>
        bind_cols(testing(roomba_split)) |>
        accuracy(truth = segment, estimate = .pred_class),
      fit_wf_dt_03 |> 
        predict(new_data = testing(roomba_split)) |>
        bind_cols(testing(roomba_split)) |>
        accuracy(truth = segment, estimate = .pred_class),
      fit_wf_dt_04 |> 
        predict(new_data = testing(roomba_split)) |>
        bind_cols(testing(roomba_split)) |>
        accuracy(truth = segment, estimate = .pred_class),
      fit_wf_dt_05 |> 
        predict(new_data = testing(roomba_split)) |>
        bind_cols(testing(roomba_split)) |>
        accuracy(truth = segment, estimate = .pred_class),
      fit_wf_dt_06 |> 
        predict(new_data = testing(roomba_split)) |>
        bind_cols(testing(roomba_split)) |>
        accuracy(truth = segment, estimate = .pred_class),
    )
  )
)
```

I can't find improved predictive fit by tuning the hyperparameters for this data, but all of this screams out for some sort of for loop or function -- maybe you've even made one!
